Cannibalism among the supermassive black holes

### 2016-08-03 paper.tex
added biblio.bib file for references; modified citations.

\subsection{Merger tree}
Where we got the merger data from and how we extracted it.
- Using Andrea Kulier's cosmological simulation, we plotted galaxy masses as a function of time.
- We took the data from the three most massive galaxies (ie, most massive at redshift z=0).
- We curve-fit each galaxy's mass to polynomial functions of time.
- We also curve-fit each galaxy's (accreted+seeded) central black hole mass to exponential functions of time.
- We added those functions to the Fortran hermite code
- We implemented the SO potential-density pair (using the m200, r200 from the fitting functions above, getting half-mass radius from NFW profile, and using it as half-mass radius for the SO profile).

@@

For the numerical simulations presented here, we used a modified version of the algorithmic chain integrator \textsc{AR-Chain} developed by \citet{Mikkola06}. It uses algorithmic chain regularization for high-precision integration of few-body dynamics, and is capable of handling velocity-dependent forces efficiently. It includes relativistic post-Newtonian terms up to order PN2.5 \citep{Mikkola08}.

@@

\subsubsection{Gravitational wave recoils}
The code \textsc{AR-Chain} includes PN terms up to order 2.5. The SMBHs can therefore merge via gravitational wave emission. We include gravitational wave recoils following the prescription outlined in \citet{Kulier_2015}, which is based on the fitting formula by \citet{Lousto12}. To save computational time, we assume that a merger will be inevitable when the separation between two SBHs gets smaller than 10\,000 Schwarzschild radii. At the moment of the merger, we assume that the spin vectors of the two SBHs are randomly aligned. This results in kick velocities of up to several thousand km\,s$^{-1}$, with a median kick of $\approx 290$\,km\,s$^{-1}$. Since our simulations focus on NSC with relatively low escape velocities, this implies that a majority of the merging SBHs escape from the NSCs.

@@

\bibliographystyle{apj}
\begin{thebibliography}{}

\bibitem[\protect\citeauthoryear{Aarseth}{2003}]{Aarseth03}
Aarseth, S.~J., 2003, Gravitational N-Body Simulations (Cambridge University Press)

\bibitem[\protect\citeauthoryear{K{\"u}pper et al.}{2011}]{Kupper11} 
K{\"u}pper, A.~H.~W., Maschberger, T., Kroupa, P., Baumgardt, H., 2011, MNRAS, 417, 2300

\end{thebibliography}
\end{document}

>>>>

\subsection{Merger tree}
- Where we got the merger data from and how we extracted it.
Our merger tree data came from cosmological simulations of Kulier
- Using Andrea Kulier's cosmological simulation, we plotted galaxy masses as a function of time.

- We took the data from the three most massive galaxies (ie, most massive at redshift z=0).

- We curve-fit each galaxy's mass to polynomial functions of time.

- We also curve-fit each galaxy's (accreted+seeded) central black hole mass to exponential functions of time.

- We added those functions to the Fortran hermite code

- We implemented the SO potential-density pair (using the m200, r200 from the fitting functions above, getting half-mass radius from NFW profile, and using it as half-mass radius for the SO profile).

@@

For the numerical simulations presented here, we used a modified version of the algorithmic chain integrator \textsc{AR-Chain} developed by \citet{2006MNRAS.372..219M}. It uses algorithmic chain regularization for high-precision integration of few-body dynamics, and is capable of handling velocity-dependent forces efficiently. It includes relativistic post-Newtonian terms up to order PN2.5 \citep{2008AJ....135.2398M}.

@@

\subsubsection{Gravitational wave recoils}
The code \textsc{AR-Chain} includes PN terms up to order 2.5. The SMBHs can therefore merge via gravitational wave emission. We include gravitational wave recoils following the prescription outlined in \citet{2015ApJ...799..178K}, which is based on the fitting formula by \citet{2012PhRvD..85h4015L}. To save computational time, we assume that a merger will be inevitable when the separation between two SBHs gets smaller than 10\,000 Schwarzschild radii. At the moment of the merger, we assume that the spin vectors of the two SBHs are randomly aligned. This results in kick velocities of up to several thousand km\,s$^{-1}$, with a median kick of $\approx 290$\,km\,s$^{-1}$. Since our simulations focus on NSC with relatively low escape velocities, this implies that a majority of the merging SBHs escape from the NSCs.

@@

\bibliographystyle{apj}
\bibliography{test}

%\begin{thebibliography}{}

%\bibitem[\protect\citeauthoryear{Aarseth}{2003}]{Aarseth03}
%Aarseth, S.~J., 2003, Gravitational N-Body Simulations (Cambridge University Press)

%\bibitem[\protect\citeauthoryear{K{\"u}pper et al.}{2011}]{Kupper11} 
%K{\"u}pper, A.~H.~W., Maschberger, T., Kroupa, P., Baumgardt, H., 2011, MNRAS, 417, 2300

%\end{thebibliography}
\end{document}
